\documentclass[UTF8]{article}
\usepackage[UTF8]{ctex}
\usepackage{color}
\usepackage{setspace}

\title{Problem and pain}
\begin{document}
\maketitle

\section{raw}

%通篇在讲普遍的道理/陈述 所以用一般现在时

Life is difficult. 

That is a great truth, one of the greatest truths. It's great because once we know it, we transcend it. 
Once we truely understand that life is difficult, then the truth is no longer matter to us.

Unfortunelly, most people are not willing to face problems in their life. Once there are problems and pains in their life, they begin to complain about life and fate as if life should be (这里用ought to 是不是不对？why？)  easy and comfortable. They complain about that there are too much trouble(s), difficult and stress (in their life) as if he is the most unfortunate man in the world. They curse the unjust fate that make (这里句子结构该怎么写) while others live a happy and freedom life. I know those kind of complains, cause I once had the same feeling.

Life is serious of trouble. Will you face it, cry on it, or bravely matrch? Will you complain and stand still. or manage to fight your way and selflessly share it to the  next generation?

Self-discipline is the solution of problems in life. One can not fix any trouble without it. Partical self-displine solve patical problems. Only comprehensive self-displine can solve all problems in life.

\section{supervised}
%\renewcommand{\baselinestretch}{2}
\setlength{\baselineskip}{2cm}

1. 人生苦难重重。

Life is difficult. 



2.这是个伟大的真理，是世界上最伟大的真理之一。它的伟大之处在于，一旦我们领悟了这句话的真谛，就能从苦难中解脱出来，实现人生的超越。

That is a great truth, one of the greatest truths. It's great because once we know it, we transcend it. 


3. 只要我们真正理解并接受了人生苦难重重的事实，那么我们就会释然，再也不会对人生的苦难耿耿于怀了。

Once we truely understand that life is difficult, then the truth is no longer matter to us. 


4.遗憾的是，大多数人却不愿意正视人生的苦难。

Unfortunelly, most people are not willing to face problems in their life. 


5.他们一遇到问题和痛苦，不是怨天尤人，就是抱怨自己命苦，仿佛人生本来就应该既舒适又顺利似的。

Once there are problems and pains in their life, they begin to complain about life and fate as if life should be (这里用ought to 是不是不对？why？)  easy and comfortable.  


6. 他们哀叹为什么会有那么多的麻烦、压力和困难，总觉得自己是世界上最不幸的人；

They complain about that there are too much trouble(s), difficult and stress (in their life) as if he is the most unfortunate man in the world. 


7. 他们诅咒命运不公，偏偏让他们自己、他们的家人、他们的部落、他们的社会阶层、他们的国家乃至他们的种族吃苦受罪，而别的人却安然无恙，过着自由而又幸福的生活。

They curse the unjust fate that make (这里句子结构该怎么写) while others live a happy and freedom life. 

8. 我非常了解这样的抱怨和诅咒，因为我也曾有过同样的感受。

I know those kind of complains, cause I once had the same feeling.

9. 人生是一连串的难题，面对它，你是哭哭啼啼，还是奋勇前进？你是束手无策地哀叹，还是积极想办法去解决，并将方法毫无保留地传给后人？

 Life is serious of trouble. Will you face it, cry on it, or bravely matrch? Will you complain and stand still. or manage to fight your way and selflessly share it to the  next generation?


10. 解决人生问题的关键在于自律。

Self-discipline is the solution of problems in life. 


11. 人若缺少自律，就不可能解决任何麻烦和问题。在某些方面自律，只能解决某些问题，全面的自律才能解决人生所有的问题

One can not fix any trouble without it. Partical self-displine solve patical problems. Only comprehensive self-displine can solve all problems in life.


\end{document}
