\documentclass[UTF-8]{ctexart}
\usepackage[UTF8]{ctex}

\begin{document}

\Section{Zh}
人生苦难重重。

这是个伟大的真理，是世界上最伟大的真理之一。它的伟大之处在于，一旦我们领悟了这句话的真谛，就能从苦难中解脱出来，实现人生的超越。只要我们真正理解并接受了人生苦难重重的事实，那么我们就会释然，再也不会对人生的苦难耿耿于怀了。

遗憾的是，大多数人却不愿意正视人生的苦难。他们一遇到问题和痛苦，不是怨天尤人，就是抱怨自己命苦，仿佛人生本来就应该既舒适又顺利似的。他们哀叹为什么会有那么多的麻烦、压力和困难，总觉得自己是世界上最不幸的人；他们诅咒命运不公，偏偏让他们自己、他们的家人、他们的部落、他们的社会阶层、他们的国家乃至他们的种族吃苦受罪，而别的人却安然无恙，过着自由而又幸福的生活。我非常了解这样的抱怨和诅咒，因为我也曾有过同样的感受。

 人生是一连串的难题，面对它，你是哭哭啼啼，还是奋勇前进？你是束手无策地哀叹，还是积极想办法去解决，并将方法毫无保留地传给后人？

 解决人生问题的关键在于自律。人若缺少自律，就不可能解决任何麻烦和问题。在某些方面自律，只能解决某些问题，全面的自律才能解决人生所有的问题。
\Section{En}

Life is difficult.
This is a great truth, one of the greatest truths. It is a great truth because once we truly see this truth, we transcend it. Once we truly know that life is difficult -- once we truly understand and accept it -- then life is no longer difficult. Because once it is accepted, the fact that life is difficult no longer matters.
Most do not fully see this truth that life is difficult. Instead they moan more or less incessantly, noisily or subtly, about the enormity of their problems, their burdens, and their difficulties as if life were generally easy, as if life should be easy. They voice their belief, noisily or subtly, that their difficulties represent a unique kind of affliction that should not be and that has somehow been especially visited upon them, or else upon their families, their tribe, their class, their nation, their race or even their species, and not upon others. I know about this moaning because I have done my share.
Life is a series of problems. Do we want to moan about them or solve them? Do we want to teach our children to solve them?
Discipline is the basic set of tools we require to solve life's problems. Without discipline we can solve nothing. With only some discipline we can solve only some problems. With total discipline we can solve all problem.
\end{document}