\documentclass[UTF8]{article}
\usepackage[UTF8]{ctex}
\usepackage{color}
\usepackage{setspace}

\title{Problem and pain}
\begin{document}
\maketitle

\section{src}
Life is difficult.

This is a great truth, one of the greatest truths. It is a great truth because once we truly see this truth, we transcend it. Once we truly know that life is difficult -- once we truly understand and accept it -- then life is no longer difficult. Because once it is accepted, the fact that life is difficult no longer matters.

Most do not fully see this truth that life is difficult. Instead they moan more or less incessantly, noisily or subtly, about the enormity of their problems, their burdens, and their difficulties as if life were generally easy, as if life should be easy. They voice their belief, noisily or subtly, that their difficulties represent a unique kind of affliction that should not be and that has somehow been especially visited upon them, or else upon their families, their tribe, their class, their nation, their race or even their species, and not upon others. I know about this moaning because I have done my share.

Life is a series of problems. Do we want to moan about them or solve them? Do we want to teach our children to solve them?

Discipline is the basic set of tools we require to solve life's problems. Without discipline we can solve nothing. With only some discipline we can solve only some problems. With total discipline we can solve all problem.
\section{google translate}
生活很艰难。

这是一个伟大的事实，是最伟大的事实之一。这是一个伟大的事实，因为一旦我们真正看到了这个真理，我们就会超越它。一旦我们真正了解生活是艰难的 - 一旦我们真正理解并接受它 - 那么生活就不再困难了。因为一旦被接受，生活困难的事实就不再重要。

大多数人都没有完全看到生活困难的真相。相反，他们或多或少地不停地，吵闹地或微妙地抱怨他们的问题的严重性，他们的负担，以及他们的困难，好像生活一般都很容易，好像生活应该很容易。他们大声或巧妙地表达了他们的信念，即他们的困难代表了一种独特的痛苦，这种痛苦不应该是，并且在某种程度上特别是在他们身上，或者他们的家庭，他们的部落，他们的阶级，他们的国家，他们的种族或甚至他们的物种，而不是其他物种。我知道这种呻吟，因为我已经完成了我的分享。

生活是一系列问题。我们想对他们抱怨或解决它们吗？我们想教我们的孩子解决它们吗？

纪律是我们解决生活问题所需的基本工具。没有纪律我们什么都不能解决。只有一些纪律，我们只能解决一些问题。完全纪律我们可以解决所有问题。

\section{supervised}
%\renewcommand{\baselinestretch}{2}
\setlength{\baselineskip}{2cm}

1. 生活很艰难。

Life is difficult.

2. 这是一个伟大的事实，是最伟大的事实之一。这是一个伟大的事实，因为一旦我们真正看到了这个真理，我们就会超越它。一旦我们真正了解生活是艰难的 - 一旦我们真正理解并接受它 - 那么生活就不再困难了。因为一旦被接受，生活困难的事实就不再重要。

This is a great gruth, one of the greatest truths. It is a great truth because once we know it, we transecond it. Once we truly see that life is difficult, once we truly understand and accept it, life is no more difficult. Because once it's accepted, the truth that life is difficult no longer matters.

3. 大多数人都没有完全看到生活困难的真相。相反，他们或多或少地不停地，吵闹地或微妙地抱怨他们的问题的严重性，他们的负担，以及他们的困难，好像生活一般都很容易，好像生活应该很容易。

Most people didn't understand the truth that life is difficult. Instead they complain, more or less, loudly or in a whisper, about their problems, their burden and their difficults, as if life is easy, as if life should be easy.

4. 他们大声或巧妙地表达了他们的信念，即他们的困难代表了一种独特的痛苦，这种痛苦不应该是，并且在某种程度上特别是在他们身上，或者他们的家庭，他们的部落，他们的阶级，他们的国家，他们的种族或甚至他们的物种，而不是其他物种。我知道这种呻吟，因为我已经完成了我的分享。

They voice their belief, noisy or subtly, that their difficulties is a unique suffering, which should not be, and especially happened to then, to their family, their group, their social class， their nation, their species, other than others. I know 
about this complaint because I have done my share.

5. 生活是一系列问题。我们想对他们抱怨或解决它们吗？我们想教我们的孩子解决它们吗？
Life is a series of questions. Do we want to complain or solve it ? Do we want to teach our children the solution of it.

6. 自律是我们解决生活问题所需的基本工具。没有自律我们什么都不能解决。只有一些自律，我们只能解决一些问题。完全自律我们可以解决所有问题。

Self-discipline is the basic set of tool that we are needed to solve life‘s problems. 
Without discipline we can solve nothing. With some disciplines we can solve some problems. With total discipline we can solve all problems. 

\end{document}
