\documentclass[UTF8]{article}
\usepackage[UTF8]{ctex}

\title{On a trip}
\begin{document}
\maketitle

800字文章 \\
要求涵盖景点介绍，旅游路线，用餐，购物等等

\section{script}

Vocabulary \\ 
\\
四川	Sichuan (Province) \\
成都	Chengdu \\
九寨沟  Jiuzhaigou \\
若尔盖草原 Zoige prairie \\
喀斯特地貌 karst topography \\
藏族的 Tibetan \\
骡马市 Luomashi Station \\
景点 place to visit, scenic spots\\
沼泽 marsh\\
悠闲地 leisurely\\
小溪 stream \\
细雨 drizzle\\
泥泞的 muddy\\

句式\\
\\
流过 flowed through\\
曲折 the road bend for too many times.\\
The weather is really disagreeable; one minute the sun shines, the next it is raining again.\\

\section{En}
%\setlength{\baselineskip}{2cm}

Sichuan is a good place to live and to travel. Because Sichuan has a temperate climate.
And There are various landforms in Sichuan Province, such as mountain,  river, lake, prairie and karst.
It makes me wonder that it is the reason that in Sichuan people have good looking and food have good teste.

I had a trip to Sichuan for about a week longer with my roommates when we were graduated from college.
We began with pandas and delicious food in Chengdu. Attracted by the scenes, we moved to  Jiuzhaigou and Zoige prairie. Finally we went back to Chengdu and moved to Chongqing for better hot pots.

We firstly, following the footprints of general tourism, visited famous historical scenic spots one by one, including Jinli Ancient Street, Chengdu Kuai Zhai Zane, Panda Base, Wuhou Temple and so on. We found that most are as boring as those in other Chinese countries. The famous places to visit had bacome shopping streets. We believed the spirit of City is in the food now. So we stayed at a hotel near Luomashi Station of Chengdu Metro for the sake of convenient transportation. And then we ate as much Chengdu-flavor food as we could.

Chengdu characteristic food is popular for its unique flavors (especially spicy) and cooked with various seasoning. Chengdu chuanchuan and hot pots are the most popular snakes among tourists. They are famous with their spicy and food's various tastes. After a game of mahjong, families and friends get together and eat hot pots happily. What a pleasure life! In contrast, Bingfen Pudding and Tofu Pudding are less famous, but my favorite two desserts. I'm so fond of them that I eat them every time whem I come back to Chengdu. 

If the color of Chengdu is chilli red and thighs white , the color of Jiuzhaigou and Zoige prairie is water blue and grass green.
Jiuzhaigou is a national park in the edge of Tibetan Plateau with karst topography. It is known for its many multi-level waterfalls, colorful lakes, and snow-capped peaks, among which the Colorful lakes is  the most attracting one. There are many famous colorful lakes in Jiuzhaigou, such as  Five Flower Lake, Mirror Lake and Reed Lake.They lay at snow mountain resembling  blue gems beauty wearing round her neck. The water is clear and blue. whose surface detailed reflects the sky. I spent for a while staring at it and watched the cloud roving and birds flying. 

There is only one mountain highway connect Jiuzhaigou with outside  world. Its name is 九曲十八弯 because the road bend for too many times.
We had to pass though it on the way to Zoige prairie. It took us 1 or 2  hours commuting there. As the altitude descrising, the scenery outside the car window graduated from mountain forest to marsh grassland.  We stopped at a marsh prairie among the hills, where a stream flowed through, no ones knows where it came from and where it gone. There were beeflows seeking for food and hanging around. The weather is really disagreeable; one minute the sun shines, the next it is drizzling again.  We walked on the grassland taking care not step in the mud carelessly.


\end{document}
